\tool: Programmable, Efficient, and Scalable \\ Secure Two-Party Computation for Machine Learning

### 2018-05-08 ccs/eval.tex
forgot

\paragraph{Scalability.}  To
illustrate the scalability of partitioning, we evaluate a
sequence of DNNs with and without partitioning
(where every layer of each DNN is a separate stage) in~\figureref{partitioning}.
For DNNs with up to 4 (hidden) layers, the performance is almost idential and the lines overlap, thereby
illustrating that partitioning did not cause any noticeable performance overheads.
Memory issues start showing up with the 5 (hidden) layer DNN and the non-partitioned implementation is slower.
DNNs with 6 or more layers fail to execute (terminate with a ``bus error").
However, the partitioned implementation scales well to even these large DNNs.

>>>>

\paragraph{Scalability.}  To
illustrate the scalability of partitioning, we evaluate a
sequence of DNNs with and without partitioning
(where every layer of each DNN is a separate stage) in~\figureref{partitioning}.
For DNNs with up to 4 (hidden) layers, the performance is almost idential and the lines overlap, thereby
illustrating that partitioning did not cause any noticeable performance overheads.
Memory issues start showing up in the non-partitioned implementation with the 5 layer DNN and it is slower.
Performance degrades rapidly thereafter and
DNNs with 6 or more layers fail to execute (terminate with a ``bus error").
However, the partitioned implementation scales well to even these large DNNs.
